Develop atlantisom wrappers

### 2020-01-16 WrapperDevelopment.Rmd
what should output look like
begin wrapper functions

1. initialize: locate model output (function to make a config file?), read in basic run parameters and species names, run_truth for all once and save output (optionally, run_truth for only one species?)

1. get assessment input data: configure survey, run all survey functions, configure fishery, run all fishery functions (how to save output?)

1. write input data for specific model: wrap functions in development for SS3, add functions for other models (ASAP, multispecies models)

>>>>

1. initialize: locate model output (function to make a config file?), read in basic run parameters and species names, run_truth for all once and save output 
    + User to make up front decision--want all species or just a subset?
    + May want multiple species that need to be split in a later step for models
    + wraps functions 
        + sourcing model config file--add function to make config file?
      + specifies top directory for source files, names key files for use later
      + load_fgs
      + load all other needed files--YOY, catch
      + run_truth
1. get assessment input data: configure survey, run all survey functions, configure fishery, run all fishery functions (how to save output?)
    + Based on decision above, save interim steps for use later
    + Need a switch for single vs multispecies estimation models?
    + Separate index and comp functions in output
    + indices:
      + create survey config file(s), default is a census of all see census_spec.R
        + survey index in biomass or numbers? (uses truth$biomass_ages vs truth$nums)
        + wraps functions create_survey, sample_survey_biomass
      + create fishery config file(s)
    + comps:
      + select age only or age and length
        + age only wraps create_survey using nums with sample_fish to get age comps
        + age and length (with weight at age)
          + create_survey followed by sample_fish, 
          + aggregateDensityData for resn and structn followed by sample_fish
          + inputs all to calc_age2length
      + catch comps wrap create_fishery_subset with sample_fish to get age comps, same as above for lengths
1. write input data for specific model: wrap functions in development for SS3, add functions for other models (ASAP, multispecies models)
    + wrap r4ss functions to read and write dat and ctl files
    + possibly start with set of dummy SS files with package (take from ss3sim?)
      + read in dat file
      + indices wrap SS_write_ts
      + comps wrap reformat_compositions, SS_write_comps, some of the checks for bin matches\
      + write full dat file
    + start with dummy ctl file (any from ss3sim?)
      + read in ctl file
      + wrap SS_write_bio using outputs of calc_Z, load_YOY, load_biolprm, load_runprm, etc
1. run specified model--automate for scenarios, save outputs 
1. skill assessment metrics: compare stored Atlantis truth with model output

### atlantisom initialize function

```{r ominit}

library(tidyverse)

om_init <- function(config = configfile){

  # Where are the atlantis output files? Consider filling with shiny app in future
  source(config)
  # needs these files, for example config file CC3config.R is:

  # d.name <- here::here("atlantisoutput","CC_2063_OA_OFF_22")
  # functional.groups.file <- "CalCurrentV3Groups.csv"
  # biomass.pools.file <- "DIVCalCurrentV3_Biol.nc"
  # biol.prm.file <- "CalCurrentV3_Biol.prm"
  # box.file <- "CalCurrentV3_utm.bgm"
  # initial.conditions.file <- "DIVCalCurrentV3_Biol.nc"
  # run.prm.file <- "CalCurrentV3_run.xml"
  # scenario.name <- "CCV3"
  # bioind.file <- "outputCCV3BiomIndx.txt"
  # catch.file <- "outputCCV3Catch.txt"

  #Load functional groups
  funct.groups <- atlantisom::load_fgs(dir=d.name,
                           file_fgs = functional.groups.file)
  #Get just the names of active functional groups
  funct.group.names <- funct.groups %>% 
    filter(IsTurnedOn == 1) %>%
    select(Name) %>%
    .$Name

  # load true catch in tons
  truecatchbio <- atlantisom::load_catch(d.name, file_catch = catch.file, fgs = funct.groups)

  # load YOY
  YOY <- atlantisom::load_yoy(d.name, paste0("output", scenario.name, "YOY.txt"))

  # load biol_prm
  biol <- atlantisom::load_biolprm(d.name, biol.prm.file)

  # load run_prm
  runpar <- atlantisom::load_runprm(d.name, run.prm.file)

  # default run_truth setup will save the file, so check for that first
  if(!file.exists(file.path(d.name, 
                            paste0("output", scenario.name, "run_truth.RData")))){
    #Store all loaded results into an R object
    truth <- atlantisom::run_truth(scenario = scenario.name,
                       dir = d.name,
                       file_fgs = functional.groups.file,
                       file_bgm = box.file,
                       select_groups = funct.group.names,
                       file_init = initial.conditions.file,
                       file_biolprm = biol.prm.file,
                       file_runprm = run.prm.file,
                       verbose = TRUE
    )
  } else {
    truth <- get(load(file.path(d.name,
                                paste0("output", scenario.name, "run_truth.RData"))))
  }

  omlist <-list("funct.groups" = funct.groups, 
                "funct.group.names" = funct.group.names,
                "truecatchbio" = truecatchbio,
                "YOY" = YOY,
                "biol" = biol,
                "runpar" = runpar,
                "truth" = truth)

  return(omlist)
}

```

Usage:

```{r exinit}

library(here)
CC3om <- om_init(here("config/CC3config.r"))

```

### Get assessment input data

Split to single species or subset of assessed species, get index data, get compositional data.

```{r inputs}

om_species <- function(species = spp, omlist){
  # spp format c("speciesname1", "speciesname2")
  if(!all(species %in% omlist$funct.group.names)) stop("species name not found") 
  species_ss <- species

  return(species_ss)
}

```

Usage:

```{r exsp}

om_species(c("Pacific_sardine"), CC3om)

```

## Cumbersome giant files eat all the memory!

Implement Christine's memory saving things from the NEMOW demo
